---
title: "Expressivness in Association to Attachment Style"
author: "Claudia Bobadilla"
date: "August 9, 2023"
output: 
  html_document:
    toc: true
    toc_float: true


---

```{r setup, include=FALSE}
#Install:install.packages("haven")
#This will allow you to upload a ".sav" file

#In addition, click the "Knit" button from the Script Window, go to "Knit Directory" and click on "Project Directory"

```

```{r Packages}
library(haven)
```

```{r LoadData}
#Load the data
labdata<-read_sav("SummerStatsFinalProject/data_ier 2.sav")
```

## Predictions
Avoidant Attachment Style

1. A participant higher in avoidant attachment style is less willing to express negative emotions.

2. A participant higher in avoidant attachment style is less willing to express positive emotions.

Anxious Attachment Style

3. A participant higher in anxious attachment style is less willing to express negative emotions.

4. A participant higher in anxious attachment style is more willing to express positive emotions.

## Descriptives

Descriptive Statistics for Expressivity
```{r}



```

```{r}

#Process
#Condense vin. #1 & 2 (postive, target's willingness to express emotion to partner)
#condense vin. #3 & 4 (negative, target's willingness to express emotion to partner)

#variables #10, 20, 30, 40



prediction1<-lm(negative_express~avoidant)
prediction2<-lm(positive_express~anxious)
prediction3<-lm(negative_express~avoidant)
prediction4<-lm(positive_express~anxious)
```

```{r}
colnames(labdata)


```

