---
title: "Expressivness in Association to Attachment Style"
author: "Claudia Bobadilla"
date: "August 9, 2023"
output: 
  html_document:
    toc: true
    toc_float: true
---
    
```{r Note, include=FALSE}
#Remember, 'html' refers to websites...this will be placed in the Github

#'toc' refers to 'Table of Contents'
#'toc_float' refers to placing the toc to the left-hand side of the page
#'include=FALSE'corresponds to not putting this in the final output
#Do not have spaces in chunk names
```


```{r Setup, include=FALSE}
#Install:install.packages("haven") in the Console window
#This will allow you to upload a ".sav" file

#In addition, click the "Knit" button from the Script Window, go to "Knit Directory" and click on "Project Directory"

```

```{r Packages}
library(haven)
```

```{r LoadData}
#Load the data
labdata<-read_sav("SummerStatsFinalProject/data_ier 2.sav")
```

## Predictions
### Negative Emotions

Avoidant attachment style will be negatively associated with negative emotions and anxious attachment style will be negatively associated with negative emotions.

### Positive Emotions

Avoidant attachment style will be negatively associated with positive emotions and anxious attachment style will be positively associated with positive emotions.

## Descriptives

```{r CondendseAndCreate}

#Process
#Condense vignette 1 & 2 (postive,target's willingness to express emotion to partner)
#condense vignette 3 & 4 (negative,target's willingness to express emotion to partner)

labdata$positive_exp<-rowMeans(labdata[,c(10,20)])
labdata$negative_exp<-rowMeans(labdata[,c(30,40)])

#"labdata$positive_exp", refers to adding a new titled column into my dataset
#"<-rowMeans(labdata[,c(10,20)])", refers to combining both scores on the positive vignettes, as each Target participant was assessed twice

#Same goes for the negative vignettes

#Here is how to check you have added these new variable or 'condensed' columns
colnames(labdata)
```

### Descriptive Statistics for Expressivity

```{r}
#Target Measure Only

#There were 4 vignettes, 2 negative and 2 positives
#Each one had 8 related emotions rated on intensity

#Target's instructions: "Imagine that you called your partner and started talking about your day. Below are short sections from your talk. Please rate the intensity of the emotions you might have experienced during the times you are talking."


#Here: Target's willingness to express emotions

 
c(summary(labdata$negative_exp),"SD"=sd(labdata$negative_exp,na.rm=T))

c(summary(labdata$positive_exp),"SD"=sd(labdata$positive_exp,na.rm=T))

#Key reminder: "na.rm=T" removes any NA values if any, scan data prior
```

### Descriptive Statistics for Attachment Styles
```{r}
#Scale used: Revised Adult Attachment Scale 

  #Two separate subscales in this questionnaire each assess avoidant and anxious            attachment style
  
      #Each participant can have different scores for each category such as: Low and high,        high and low, high and high, or low and low variations

c(summary(labdata$Target_Attachment_Avoidance),"SD"=sd(labdata$Target_Attachment_Avoidance,na.rm=T))

c(summary(labdata$Target_Attachment_Anxiety),"SD"=sd(labdata$Target_Attachment_Anxiety,na.rm=T))
```


## Prediction 1

```{r P1}

p1<-lm(negative_exp~Target_Attachment_Avoidance+Target_Attachment_Anxiety, data=labdata)

summary(p1)

#Generate the Graph
  #Install "reshape2" in the console window
  #Load package

library(reshape2)

#Purpose of melting data: combines to incorporate into the ggplot
labMelt<-melt(labdata,measure.vars=c("Target_Attachment_Avoidance","Target_Attachment_Anxiety"),
              variable.name=c("Attachment_Style"),value.name="Attachment_Score")

#Load (but remember to install ggplot2)
library(ggplot2)

plotp1<-ggplot(data=labMelt,
              aes(x=Attachment_Score,
                  y=negative_exp,
                  color=Attachment_Style))+
  labs(x="Attachment Score",
       y="Negative Expressivity",
       color="Attachment Style")+
  geom_jitter()+
  geom_smooth(method="lm")+
  theme_gray(base_size=10)
  scale_color_discrete(labels=c("Avoidance","Anxiety"))

#Output the graph

plotp1

```

Prediction 2
```{r P2}
p2<-lm(positive_exp~Target_Attachment_Avoidance+Target_Attachment_Anxiety, data=labdata)

summary(p2)

#Purpose of melting data: combines to incorporate into the ggplot
labMelt<-melt(labdata,measure.vars=c("Target_Attachment_Avoidance","Target_Attachment_Anxiety"),
              variable.name=c("Attachment_Style"),value.name="Attachment_Score")


# Generate Graph
plotp2<-ggplot(data=labMelt,
              aes(x=Attachment_Score,
                  y=positive_exp,
                  color=Attachment_Style))+
  labs(x="Attachment Score",
       y="Positive Expressivity",
       color="Attachment Style")+
  geom_jitter()+
  geom_smooth(method="lm")+
  theme_gray(base_size=10)
  scale_color_discrete(labels=c("Avoidance","Anxiety"))

#Output the graph

plotp2

```



