---
title: "Expressivness in Association to Attachment Style"
author: "Claudia Bobadilla"
date: "August 9, 2023"
output: 
  html_document:
    toc: true
    toc_float: true
    
```{r Note, include=FALSE}
#Remember, 'html' refers to websites...this will be placed in the Github

#'toc' refers to 'Table of Contents'
#'toc_float' refers to placing the toc to the left-hand side of the page
```


```{r setup, include=FALSE}
#Install:install.packages("haven")
#This will allow you to upload a ".sav" file

#In addition, click the "Knit" button from the Script Window, go to "Knit Directory" and click on "Project Directory"

```

```{r Packages}
library(haven)
```

```{r LoadData}
#Load the data
labdata<-read_sav("SummerStatsFinalProject/data_ier 2.sav")
```

##Predictions

##Negative Emotions

A participant higher in avoidant attachment style and lower in anxious attachment style is less willing to express negative emotions.

A participant higher in anxious attachment style and lower in avoidant attachment style is less willing to express negative emotions.

##Positive Emotions

A participant higher in avoidant attachment style and lower in anxious attachment style is less willing to express positive emotions.

A participant higher in anxious attachment style and lower in avoidant attachment style is more willing to express positive emotions.

## Descriptives

Descriptive Statistics for Expressivity
```{r}
#Target
#Scale used: 
summary(labdata$negative_exp)
summary(labdata$positive_exp)
```

Descriptive Statistics for Attachment Styles
```{r}
#Target
#Scale used:Revised Adult Attachment Scale 
summary(labdata$Target_Attachment_Avoidance)
summary(labdata$Target_Attachment_Anxiety)
```



```{r Condense and Create}

#Process
#Condense vignette 1 & 2 (postive,target's willingness to express emotion to partner)
#condense vignette 3 & 4 (negative,target's willingness to express emotion to partner)

labdata$positive_exp<-rowMeans(labdata[,c(10,20)])
labdata$negative_exp<-rowMeans(labdata[,c(30,40)])

#"labdata$positive_exp", refers to adding a new titled column into my dataset
#"<-rowMeans(labdata[,c(10,20)])", refers to combining both scores on the positive vignettes, as each Target participant was assessed twice

#Same goes for the negative vignettes

#Here is how to check you have added these new variable or 'condensed' columns
colnames(labdata)
```

Prediction 1
```{r P1}

p1<-lm(negative_exp~Target_Attachment_Avoidance+Target_Attachment_Anxiety, data=labdata)

summary(p1)
```

Prediction 2
```{r P2}
p1<-lm(negative_exp~Target_Attachment_Avoidance+Target_Attachment_Anxiety, data=labdata)

summary(p1)


```

Prediction 3
```{r P3}



```

Prediction 4
```{r P4}



```